Univalent Universes and Completness of Reversible Programs: \\ Featherweight HoTT

### 2017-03-06 upi.tex
correcting notation

\makeatletter
\tikzset{my loop/.style =  {to path={
  \pgfextra{\let\tikztotarget=\tikztostart}
%%  [looseness=100, in=60,out=120]
%%  [looseness=8,min distance=5mm, in=60,out=120]
  \tikz@to@curve@path}
  }}
\makeatletter

@@

\paragraph*{Univalent Type Family.}
Given standard constructions in the book, we have a function:
\[\begin{array}{rcl}
\textit {transport-equiv} &:& \Pi_{P : A \to \mathcal{U}}~ \Pi_{x,y:A}~
    x \equiv y  \to P x \simeq P y \\
\textit{transport-equiv}~P~x~y &=& \lambda p. \mathit{idtoequiv}(\mathit{ap}_{P}(p))
\end{array}\]
with the standard definitions for
$\mathit{ap} : (x \equiv y) \to (P(x) \equiv P(y))$ and
$\mathit{idtoequiv} : (A \equiv B) \to (A \simeq B)$. We say a type family
$P : A \to \mathcal{U}$ is \emph{univalent} if for all $x,y:A$
the function $\textit{transport-equiv}~P~x~y$ is an equivalence. Formally:
\[\begin{array}{l}
\textit{is-univalent-fibration} : (A \to \mathcal{U}) \to \mathcal{U} \\
\textit{is-univalent-fibration}~P = \Pi_{(x,y:A)} \textit{is-equiv}~(\textit{transport-equiv}~P~x~y)
\end{array}\]

\noindent\paragraph*{Examples}
\begin{itemize}
\item Take $A = \mathcal{U}$ and $P = \mathit{Id}_{\mathcal{U}}$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to $\Pi_{x,y:\mathcal{U}}~x \equiv y \to
  x \simeq y$ which is the usual definition of univalence.

>>>>

@@

\paragraph*{Univalent Type Family.}
Given standard constructions in the book, we have a function:
\[\begin{array}{rcl}
\textit {transport-equiv} &:& \Pi_{(P : A \to \mathcal{U})}~ \Pi_{(x,y:A)}~
    x \equiv y  \to P x \simeq P y \\
\textit{transport-equiv}~P~x~y &=& \lambda p. \mathit{idtoeqv}(\mathit{ap}_{P}(p))
\end{array}\]
with the standard definitions for
$\mathit{ap} : (x \equiv y) \to (P(x) \equiv P(y))$ and
$\mathit{idtoeqv} : (A \equiv B) \to (A \simeq B)$. We say a type family
$P : A \to \mathcal{U}$ is \emph{univalent} if for all $x,y:A$
the function $\textit{transport-equiv}~P~x~y$ is an equivalence. Formally:
\[\begin{array}{l}
\textit{is-univalent-fibration} : (A \to \mathcal{U}) \to \mathcal{U} \\
\textit{is-univalent-fibration}~P = \Pi_{(x,y:A)} \textit{is-equiv}~(\textit{transport-equiv}~P~x~y)
\end{array}\]

\noindent\paragraph*{Examples}
\begin{itemize}
\item Take $A = \mathcal{U}$ and $P = \mathit{Id}_{\mathcal{U}}$. The statement
  $\textit{is-univalent-fibration}~P$ reduces to
  $\Pi_{(x,y:\mathcal{U})}~\textit{is-equiv}~\mathit {idtoeqv}$ which is the
  usual definition of univalence.
